Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-05-17 paper/paper_backup.tex
[major] add double blind paper and review comments

% ISBN
\acmISBN{000-0000-00-000/00/00}

@@

\begin{equation}
	\dot{v}(t) = \frac{\partial}{\partial t} v(t) = \frac{\partial}{\partial t} \frac{\partial}{\partial t} x(t)
\end{equation}

@@

To evaluate this experiment, we performed it many times and monitored trajectory generated by DMP system. We defined angle of inclination as the angle between arm of mannequin and horizontal axis. The angle of inclination is defined in clockwise direction, hence it is +ve when arms are inclined upward, similarly it is -ve when arms are inclined downward as shown in figure \ref{fig:inclination}. It was changed by keeping arms at various heights. The angle of inclination for horizontal  orientation is refereed as 0 degree. For each angle of inclination, we performed the experiment 6 times. We then changed the angle of inclination by 5 degree step size and followed the same steps as described above. We stopped this experiment, once we noticed a huge degradation in success rate, such as success rate close to zero. The accuracy measurement is shown in figure \ref{fig:accuracy}. It was observed that DMP system was able to generate the appropriate trajectory for a range of $20^\circ$ and it never failed in this range. However, as we keep on going far away from the original posture, success rate starts declining and finally reached to $0$.

@@

The clothing task has to deal with complex dynamics including manipulation of clothing article. Clothes are non-rigid, flexible and highly deformable objects, making the task more difficult to perform. During the task, we observed forces being applied at both the end-effector of Baxter robot. Trajectories were monitored and categorized into two \textit{success} and \textit{failure}. The mean of these two categories is calculated and plotted as shown in figure \ref{fig:position_force}. Force value is the norm of force applied in all three cartesian directions. This is the average profile over several \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.

>>>>

% ISBN
\acmISBN{1-58113-000-0/00/0010}

@@

\begin{equation}
	\dot{v}(t) = \frac{\partial v}{\partial t} = \frac{\partial^2 x}{\partial t^2}
\end{equation}

@@

To evaluate this experiment, we performed it 9 times for each angle of inclination and monitored trajectory generated by DMP system. We defined angle of inclination as the angle between arm of mannequin and horizontal axis. The angle of inclination is defined in clockwise direction, hence it is +ve when arms are inclined upward, similarly it is -ve when arms are inclined downward as shown in figure \ref{fig:inclination}. It was changed by keeping arms at various heights. The angle of inclination for horizontal  orientation is refereed as 0 degree. For each angle of inclination, we performed the experiment 6 times. We then changed the angle of inclination by 5 degree step size and followed the same steps as described above. We stopped this experiment, once we noticed a huge degradation in success rate, such as success rate close to zero. The accuracy measurement is shown in figure \ref{fig:accuracy}. It was observed that DMP system was able to generate the appropriate trajectory for a range of $20^\circ$ and it never failed in this range. However, as we keep on going far away from the original posture, success rate starts declining and finally reached to $0$.

@@

The clothing task has to deal with complex dynamics including manipulation of clothing article. Clothes are non-rigid, flexible and highly deformable objects, making the task more difficult to perform. During the task, we observed forces being applied at both the end-effector of Baxter robot. Trajectories were monitored and categorized into two \textit{success} and \textit{failure}. The mean of these two categories is calculated and plotted as shown in figure \ref{fig:position_force}. Force value is the norm of force applied in all three cartesian directions. This is the average profile over 6 \textit{success} and \textit{failure} trajectories for different postures of left arm of mannequin.
